---
title: "296B Presentation - ER"
output: html_document
date: "2023-03-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#setwd("/Users/zexing/Desktop/296B Final/")
#rm(list=ls())
```

```{r, message = FALSE}
library(lubridate)
library(ggplot2)
library(kableExtra)
library(tidyverse)
library(dplyr)
library(readxl, lib.loc = "/Library/Frameworks/R.framework/Versions/4.2/Resources/library")
```




#### Part II: Equity Risk Premium based on UST-1M

$$
Equity\;Risk\; Premium = \frac{Large\;Cap\;TR}{US\;Treasury\;TR_{1mo}}-1
$$

**SBBI - 1926.1.1 to 2022.12.01**
```{r, message = FALSE}
sbbi_large_cap <- read_excel("/Users/zexing/Desktop/296B Final/Historical Data/SBBI Data for Capital Markets (2022_12_31).xlsx", sheet = "large_cap") %>%
  rename("obs_date" = 1, "sbbi_large_cap" = 2,
         "ust_1m" = 3, "sbbi_equity_return" = 4, "cpi" = 5) %>%
  mutate(obs_date = as.Date(obs_date,origin = "1899-12-30"))
```

*Summary of the overall distribution*
```{r}
summary(sbbi_large_cap$sbbi_equity_return)
sbbi_large_cap %>%
  ggplot(aes(x=sbbi_equity_return))+
  geom_histogram(aes(y=..density..),color = "grey")+
  labs(x = "Distribution of Mean of Historical Equity Return (Annual)")
```

*Bucket based on inflation*
```{r,results="hide"}
sbbi_large_cap <- sbbi_large_cap[order(sbbi_large_cap$cpi),]
sum(sbbi_large_cap$cpi <=0)
sum((sbbi_large_cap$cpi >0) & (sbbi_large_cap$cpi<=0.025))
sum((sbbi_large_cap$cpi >0.025) & (sbbi_large_cap$cpi<=0.05))
sum(sbbi_large_cap$cpi >=0.05)
sbbi_large_cap <- sbbi_large_cap %>%
  mutate(bucket = c(rep("Deflation",10),
                    rep("Low",35),
                    rep("Medium",33),
                    rep("High",18)))
#sbbi_large_cap <- sbbi_large_cap[order(sbbi_large_cap$obs_date),]
```

*Mean of Equity Return within Inflation Bucket*
```{r}
sbbi_er_mean <- sbbi_large_cap %>%
	group_by(bucket) %>%
	summarise(sbbi_er_mean = mean(sbbi_equity_return))
sbbi_er_mean <- sbbi_er_mean[c(1,3,4,2),]
sbbi_er_mean
```

**NAIC - 100 Years of Data(Given)**

*First load all the data*
```{r}
naic_large_cap <- read.csv("/Users/zexing/Desktop/296B Final/NAIC/naic_large_cap_tr.csv")
naic_large_cap <- naic_large_cap[,-1]

naic_ust_1m <-read.csv("/Users/zexing/Desktop/296B Final/NAIC/naic_ust_1m.csv")
naic_ust_1m <- naic_ust_1m[,-1]
summary(unlist(naic_ust_1m))
```

*Convert to Annual Data*
```{r}
naic_large_cap_annual <- data.frame(matrix(1000, ncol=1, nrow = 1000))
for (i in 1:1200){
  naic_large_cap_annual[,i+1] <- naic_large_cap_annual[,i]*(1+naic_large_cap[,i])
}
holder <- data.frame(matrix(0, ncol=100, nrow = 1000))
for (i in 1:100){
  holder[,i] <- naic_large_cap_annual[,1+12*i]/naic_large_cap_annual[,(1+12*(i-1))]-1
}
naic_large_cap_annual <- holder
```

```{r}
summary(sbbi_large_cap$sbbi_large_cap)
summary(unlist(naic_large_cap_annual))
```


```{r}
naic_ust_1m_annual <- data.frame(matrix(1000, ncol=1, nrow = 1000))
for (i in 1:1200){
  naic_ust_1m_annual[,i+1] <- naic_ust_1m_annual[,i]*(1+naic_ust_1m[,i]/12)
}
holder <- data.frame(matrix(0, ncol=100, nrow = 1000))
for (i in 1:100){
  holder[,i] <- naic_ust_1m_annual[,1+12*i]/naic_ust_1m_annual[,(1+12*(i-1))]-1
}
naic_ust_1m_annual <- holder
```

```{r}
summary(sbbi_large_cap$ust_1m)
summary(unlist(naic_ust_1m_annual))
```

*Then calculate the Equity Return. The formula is (1+large_cap)/(1+ust_1m) - 1*
```{r}
naic_er_annual <- data.frame(matrix(0, ncol=100, nrow = 1000))
for (col in 1:100){
  for (row in 1:1000){
    naic_er_annual[row,col] = (1+naic_large_cap_annual[row,col])/(1+naic_ust_1m_annual[row,col]) - 1
  }
}
```


```{r}
summary(sbbi_large_cap$sbbi_equity_return)
summary(unlist(naic_er_annual))
x <- unlist(naic_er_annual)
quantile(x,0.01)
quantile(x,0.05)
quantile(x,0.1)
quantile(x,0.9)
quantile(x,0.95)
quantile(x,0.99)


quantile(sbbi_large_cap$sbbi_equity_return,0.01)
quantile(sbbi_large_cap$sbbi_equity_return,0.05)
quantile(sbbi_large_cap$sbbi_equity_return,0.1)
quantile(sbbi_large_cap$sbbi_equity_return,0.9)
quantile(sbbi_large_cap$sbbi_equity_return,0.95)
quantile(sbbi_large_cap$sbbi_equity_return,0.99)
```


```{r}
mean_container <- numeric(1000)
for (i in 1:1000){
  mean_container[i] = mean(t(as.tibble(naic_er_annual[i,])))
}
mean_container <- as.tibble(mean_container)
mean_container %>%
  ggplot(aes(x=value)) +
  geom_histogram(aes(y=..density..),color = "grey") +
    labs(x = "Distribution of Mean of NAIC Simulated Equity Return (Annual)")
```

**AIRG - 69 Years of Data 1954.1 - 2022.12**

**AIRG Large Cap (Annual)**
```{r}
airg_large_cap <- read.csv("/Users/zexing/Desktop/296B Final/AIRG/airg_large_cap_annual.csv",header = FALSE)
holder <- data.frame(matrix(0, ncol=70, nrow = 1000))
for (col in 1:70){
  holder[,col] = airg_large_cap[,col+1]/airg_large_cap[,col]-1
}
airg_large_cap <- holder[,-70]
```

**UST - 3M (Annual)**
```{r, message = FALSE}
airg_ust_3m <- read.csv("/Users/zexing/Desktop/296B Final/AIRG/airg_ust_3m_annual.csv",
                          header = FALSE) 
airg_ust_3m <-  airg_ust_3m[,-c(1,71)]
summary(unlist(airg_ust_3m))
```

*Then calculate the Equity Return. The formula is (1+large_cap)/(1+ust_3m) - 1*
```{r}
airg_er_annual <- data.frame(matrix(0, ncol=69, nrow = 1000))
for (col in 1:69){
  for (row in 1:1000){
    airg_er_annual[row,col] = (1+airg_large_cap[row,col])/(1+airg_ust_3m[row,col]) - 1
  }
}
summary(unlist(airg_er_annual))
```


```{r}
x <- unlist(airg_er_annual)
quantile(x,0.01)
quantile(x,0.05)
quantile(x,0.1)
quantile(x,0.9)
quantile(x,0.95)
quantile(x,0.99)
```


```{r}
mean_container <- numeric(1000)
for (i in 1:1000){
  mean_container[i] = mean(t(as.tibble(airg_er_annual[i,])))
}
mean_container <- as.tibble(mean_container)
mean_container %>%
  ggplot(aes(x=value)) +
  geom_histogram(aes(y=..density..),color = "grey") +
    labs(x = "Distribution of Mean of AIRG Simulated Equity Return (Annual)")
```


```{r}
sbbi_large_cap %>%
  ggplot(aes(x=sbbi_equity_return)) +
  geom_histogram(aes(y=..density..),color = "grey") +
  labs(x = "SBBI - Equity Risk Premium")

naic_er_annual_v <- as.tibble(unlist(naic_er_annual))
naic_er_annual_v%>%
  ggplot(aes(x=value)) +
  geom_histogram(aes(y=..density..),color = "grey") +
  labs(x = "NAIC - Equity Risk Premium")

airg_er_annual_v <- as.tibble(unlist(airg_er_annual))
airg_er_annual_v %>%
  ggplot(aes(x=value)) +
  geom_histogram(aes(y=..density..),color = "grey") +
  labs(x = "AIRG - Equity Risk Premium")
```

























