---
title: "296B - NAIC Cleaning"
output: html_document
date: "2023-02-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r, message = FALSE}
#rm(list = ls())
library(lubridate)
library(ggplot2)
library(kableExtra)
library(tidyverse)
library(dplyr)
library(gridBase)
library(gridExtra)
```

#### PART 0: NAIC Cleaning

**Load the original data and take out unnecessary info**
```{r,eval = FALSE}
naic <- read.csv("/Users/zexing/Desktop/model comparison/NAIC/1000_Path_Subset_1a_Conning_GFF_Baseline_Equity_123121.csv", header = TRUE)
naic <- naic[,-c(3:35)] #get rid of spot rates
naic <- naic[,-c(5:24)] #Only keep 1mo,3mo,20year
naic <- naic[,-c(6:15)]
naic <- naic[,-c(24:39)]
naic <- naic[,-c(17:21)]
naic <- naic[,-c(8:11)]
naic <- naic[,-c(12)]
write.csv(naic, file = "naic_cleaning.csv")
```

**Further clean the data to make it more concise**
```{r,eval = FALSE}
naic_c <- read.csv("/Users/zexing/Desktop/296B Final/RAW DATA/naic_cleaning.csv",header = TRUE)
naic_c <- naic_c %>%
  mutate(int_govt_tr = Int.Govt.Bonds.Price + Int.Govt.Bonds.Income) %>%
  mutate(short_govt_tr = Short.Govt.Bonds.Price + Short.Govt.Bonds.Income) %>%
  mutate(lt_govt_tr = Long.Govt.Bonds.Price + Long.Govt.Bonds.Income) %>%
  mutate(large_cap_tr = Large.Cap.Price + Large.Cap.Income)
naic_c <- naic_c[,-c(7:14)]
naic_c <- naic_c %>%
  rename("ust_1m_yield" = 4,
         "ust_3m_yield" = 5,
         "ust_20yr_yield" = 6)
write.csv(naic_c, file = "naic_final.csv")
```

**Load our final data**
```{r}
naic <- read.csv("/Users/zexing/Desktop/model comparison/NAIC/naic_final.csv",header = TRUE)
naic <- naic[,-c(1:2)]
```

 **Create a list that store all the values correspondent to I_th time**
```{r}
time <- c(1:1200)
path <- c(1:1000)

# Each object contains 1000 values
mylist <- list()
for (i in time) {
  mylist[[i]] <- which(naic$TIME == i)
}
```

**Get UST-1m NAIC Simulated Data**
```{r}
df <- data.frame(matrix(ncol = 1200, nrow = 1000))
for (col in time) {
  for (row in path) {
    df[row,col] <- naic$ust_1m_yield[mylist[[col]][[row]]]
  }
}
write.csv(df, file = "naic_ust_1m.csv")
```

```{r}
# Check we do this correctly
which(naic$TIME == 4)
naic$ust_1m_yield[10814] #10th simulation, time 4
df[10,4] #10th simulation, time 4
# Number match! Did this correctly!
```

**Get UST-3m NAIC Simulated Data**
```{r}
df1 <- data.frame(matrix(ncol = 1200, nrow = 1000))
for (col in time) {
  for (row in path) {
    df1[row,col] <- naic$ust_3m_yield[mylist[[col]][[row]]]
  }
}
write.csv(df1, file = "naic_ust_3m.csv")
```

```{r}
# Check we do this correctly
which(naic$TIME == 4)
naic$ust_3m_yield[10814] #10th simulation, time 4
df1[10,4] #10th simulation, time 4
# Number match! Did this correctly!
```

**Get UST-20Yr NAIC Simulated Data**
```{r}
df2 <- data.frame(matrix(ncol = 1200, nrow = 1000))
for (col in time) {
  for (row in path) {
    df2[row,col] <- naic$ust_20yr_yield[mylist[[col]][[row]]]
  }
}
write.csv(df2, file = "naic_ust_20yr.csv")
```

```{r}
# Check we do this correctly
which(naic$TIME == 4)
naic$ust_20yr_yield[10814] #10th simulation, time 4
df2[10,4] #10th simulation, time 4
# Number match! Did this correctly!
```

**Get Intermediate Govt Bond TR NAIC Simulated Data**
```{r}
df3 <- data.frame(matrix(ncol = 1200, nrow = 1000))
for (col in time) {
  for (row in path) {
    df3[row,col] <- naic$int_govt_tr[mylist[[col]][[row]]]
  }
}
write.csv(df3, file = "naic_int_govt_tr.csv")
```

```{r}
# Check we do this correctly
which(naic$TIME == 4)
naic$int_govt_tr[10814] #10th simulation, time 4
df3[10,4] #10th simulation, time 4
# Number match! Did this correctly!
```

**Get Short Term Govt Bond TR NAIC Simulated Data**
```{r}
df4 <- data.frame(matrix(ncol = 1200, nrow = 1000))
for (col in time) {
  for (row in path) {
    df4[row,col] <- naic$short_govt_tr[mylist[[col]][[row]]]
  }
}
write.csv(df4, file = "naic_short_govt_tr.csv")
```

```{r}
# Check we do this correctly
which(naic$TIME == 4)
naic$short_govt_tr[10814] #10th simulation, time 4
df4[10,4] #10th simulation, time 4
# Number match! Did this correctly!
```

**Get Long Term Govt Bond TR NAIC Simulated Data**
```{r}
df5 <- data.frame(matrix(ncol = 1200, nrow = 1000))
for (col in time) {
  for (row in path) {
    df5[row,col] <- naic$lt_govt_tr[mylist[[col]][[row]]]
  }
}
write.csv(df5, file = "naic_lt_govt_tr.csv")
```

```{r}
# Check we do this correctly
which(naic$TIME == 4)
naic$lt_govt_tr[10814] #10th simulation, time 4
df5[10,4] #10th simulation, time 4
# Number match! Did this correctly!
```

**Get Large Cap TR NAIC Simulated Data**
```{r}
df6 <- data.frame(matrix(ncol = 1200, nrow = 1000))
for (col in time) {
  for (row in path) {
    df6[row,col] <- naic$large_cap_tr[mylist[[col]][[row]]]
  }
}
write.csv(df6, file = "naic_large_cap_tr.csv")
```

```{r}
# Check we do this correctly
which(naic$TIME == 4)
naic$large_cap_tr[10814] #10th simulation, time 4
df6[10,4] #10th simulation, time 4
# Number match! Did this correctly!
```






